Results

### 2025-10-04 index.qmd
update stats figures with new plots and visualizations

![Comparision map of (normalized) thickness and (normalized) current density](figures/enc7/thickness_current.svg){#fig-comp-map}

>>>>

![](figures/overview-7-all.pdf){#fig-overview}

![](figures/properties_hist-mva.pdf){#fig-properties-hist}

![](figures/joint_properties-mva.pdf){#fig-joint-properties}

![](figures/Alfvenicities.pdf)

![](figures/Q_sonnerup_joint_dist_den.pdf)

![](figures/B_n_ω_subset=true.pdf)

### 2025-10-04 notebooks/00_index.qmd
update stats figures with new plots and visualizations

psp_df = @rsubset(df, :id == "PSP"; view=true)
wind_df = @rsubset(df, :id == "Wind"; view=true)
thm_df = @rsubset(df, :id == "THEMIS"; view=true)p -
         thm_conf["B"] = unitify("nT") ∘ thm_conf["B"]
```

```{julia}
compute_PSP_anisotropy_params!(psp_df)
for enc in 7:9
    (tmin_psp, tmax_psp), (tmin_wind, tmax_wind) = get_timerange(enc)
    wind_df_enc = @rsubset(wind_df, :enc == enc; view=true)
    compute_Wind_anisotropy_params!(wind_df_enc, tmin_wind, tmax_wind)
end
```

@@

```{julia}
psp_B = set(tnorm_combine ∘ PSP.B_1MIN; ylabel=𝒀.B, labels=𝑳.B_RTN)
psp_V = set(PSP.V; ylabel=𝒀.V, labels=𝑳.V_RTN)
psp_n = PSP.n_spi

wind_B = set(tnorm_combine ∘ Wind.B_GSE_1MIN; ylabel=𝒀.B, labels=𝑳.B_XYZ)
wind_V = replace_outliers! ∘ set(Wind.V_GSE_K0; ylabel=𝒀.V, labels=𝑳.V_XYZ)
wind_n = set(Wind.n_p_K0; ylabel=𝒀.n, yscale=identity)
```

@@

```{julia}
# using CairoMakie
# CairoMakie.activate!()

update_theme!(; Lines=(linewidth=1, alpha=0.9), figure_padding=(1, 1, 1, 15))

add_vl_ratio = true

for enc in 7:7
    (tmin_psp, tmax_psp), (tmin_wind, tmax_wind) = get_timerange(enc)
    legend = (; position=Top())
    labels = '1':'9'
    padding = (0, 30, 0, -30)
    f = Figure(; size=(1000, 800))
    fname = "overview-$enc"
    if add_vl_ratio
        fname = "overview-vl-$enc"
        faxs = plot_PSP(f[1, 1], tmin_psp, tmax_psp, get_vl_ratio_ts(psp_df)...; legend)
        modify_faxs_base!(faxs)
        faxs = plot_Wind(f[1, 2], tmin_wind, tmax_wind - Day(1), get_vl_ratio_ts(wind_df)...; legend)
        modify_faxs_base!(faxs)
    end

    add_labels!(f[1, 1]; labels, open="(a.", padding)
    add_labels!(f[1, 2]; labels, open="(b.", padding)
    display(f)
    easy_save("overview-$enc-all")

    # tplot(f[1, 3], _tmask! .∘ tvars_themis, tmin_wind, tmax_wind; legend)
    # add_labels!(f[1, 3]; labels, open="(c.")
end
```

@@

```{julia}
using Discontinuity: ids_finder
tau = Second(30)
psp_events = ids_finder(PSP.B, tmin_psp, tmax_psp, tau)
wind_events = ids_finder(Wind.B_GSE, tmin_wind, tmax_wind, tau, Wind.V_GSE, Wind.n_p)
thm_events = ids_finder(THEMIS.B_FGL_GSE, tmin_wind, tmax_wind, tau)
```

>>>>

psp_df = @rsubset(df, :id == "PSP"; view=true)
wind_df = @rsubset(df, :id == "Wind"; view=true)
thm_df = @rsubset(df, :id == "THEMIS"; view=true)
```

```{julia}
compute_PSP_anisotropy_params!(psp_df)
for enc in 7:9
    tmin_wind, tmax_wind = get_timerange(enc)[2]
    wind_df_enc = @rsubset(wind_df, :enc == enc; view=true)
    compute_Wind_anisotropy_params!(wind_df_enc, tmin_wind, tmax_wind)

    thm_df_enc = @rsubset(thm_df, :enc == enc; view=true)
    compute_THM_anisotropy_params!(thm_df_enc, tmin_wind, tmax_wind)
end
```

@@

@@

```{julia}
update_theme!(; Lines=(linewidth=1, alpha=0.9), figure_padding=(1, 1, 1, 15))

for enc in 7:9
    (tmin_psp, tmax_psp), (tmin_wind, tmax_wind) = get_timerange(enc)
    legend = (; position=Top())
    labels = '1':'9'
    padding = (0, 30, 0, -30)
    f = Figure(; size=(1000, 800))
    faxs = plot_PSP(f[1, 1], tmin_psp, tmax_psp, get_vl_ratio_ts(psp_df)...; legend)
    modify_faxs_base!(faxs)
    faxs = plot_Wind(f[1, 2], tmin_wind, tmax_wind - Day(1), get_vl_ratio_ts(wind_df)...; legend)
    modify_faxs_base!(faxs)

    add_labels!(f[1, 1]; labels, open="(a.", padding)
    add_labels!(f[1, 2]; labels, open="(b.", padding)
    display(f)
    easy_save("overview-$enc-all")
end
```

@@

```{julia}
using Dates
using Discontinuity: ids_finder
tau = Second(30)
psp_events = ids_finder(PSP.B, tmin_psp, tmax_psp, tau)
wind_events = ids_finder(Wind.B_GSE, tmin_wind, tmax_wind, tau, Wind.V_GSE, Wind.n_p)
thm_events = ids_finder(THEMIS.B_FGL_GSE, tmin_wind, tmax_wind, tau)
```

### 2025-10-04 notebooks/02_stats.qmd
update stats figures with new plots and visualizations

```{julia}
using Dates
using StatsBase, Statistics
using PSPAnisotropy
import Discontinuity as DC
using Discontinuity: var_mapping, compute_params!, filter_low_mva_quality
using Discontinuity: compute_Alfvenicity_params!, Alfven_velocity
using DimensionalData
using DataFrames, DataFramesMeta
using CairoMakie
using Beforerr: _theme_legend, easy_save
using AlgebraOfGraphics
import AlgebraOfGraphics as AoG
using LinearAlgebra
using Accessors
using Unitful
Unitful.preferunits(u"nA", u"km")

# https://github.com/MakieOrg/AlgebraOfGraphics.jl/issues/464
foreach([:log10, :log2, :log]) do f
    @eval import Base: $f
    @eval $f(x::Unitful.Quantity) = $f(ustrip(x))
end
set_Z_theme!()
formats = (:pdf,:png)
```

@@

fs = map([:mva]) do 𝐧
    figure = (; size=(650, 400))
    𝒎 = var_mapping(; 𝐧)

@@

    tdf = @chain df begin
        @subset(.!isnan.(:L_n_mva_norm); view=true)
        # @rsubset(((:id == "PSP") && :tau <= Second(2)) || (:id != "PSP" && :tau > Second(2))) # select current sheet events with tau <= 2s for PSP and tau > 2s for Earth
        subset_𝐧(𝐧)
        dropmissing(:L_n_mva_norm)
    end

    vars = [𝒎.l_log, 𝒎.l_norm_log, 𝒎.j_log, 𝒎.j_norm_log, :Δ𝐁 => log10 => L"\text{Log }|Δ𝐁|", :Δ𝐁_norm => log10 => L"\text{Log } |Δ𝐁|/B",]
    labels = ["Thickness", "Normalized thickness", "Current density", "Normalized current density", "|Δ𝐁|", "|Δ𝐁|/B"]
    # append!(vars, [ :Δ𝐁_fit => log10 => "Log Δ𝐁_fit", :Δ𝐁_fit_norm => log10 => "Log Δ𝐁_fit_norm"])
    # append!(labels, ["Δ𝐁_fit", "Δ𝐁_fit_norm"])

    plt =
        data(tdf) *
        mapping(vars, layout=AoG.dims(1) => renamer(labels)) *
        # mapping(vars, row=AoG.dims(1) => renamer(labels), col=:type) *
        mapping(color=:id, linestyle=:enc) *
        AoG.density(; datalimits) * visual(Lines)
    draw(plt, scales(Layout=(; palette=wrapped(cols=4, by_col=true))); axis=(; yscale=log10), figure)
    easy_save("$fname-$𝐧"; formats, force=true)
end
fs[1]
```

@@

tdf = @chain df begin
    @subset(.!isnan.(:V_l_ratio); view=true)
    subset_𝐧(𝐧)
    dropmissing(:V_l_ratio)
end

vars = [:Q_sonnerup => abs => "", :ΔV_ratio => identity => "", :V_l_ratio => identity => "", :V_l_ratio_max => identity => ""]
# 𝒎.v_l_ratio, 𝒎.bn
labels = ["Q_sonnerup", "Δ V ratio", "ΔV_l ratio", "Max ΔV_l ratio"]

plt =
    data(tdf) *
    mapping(vars, row=AoG.dims(1) => renamer(labels)) *
    #   mapping(vars, col=:tau, row=AoG.dims(1) => renamer(labels)) *
    mapping(color=:id, linestyle=:enc) *
    AoG.density(; datalimits) * visual(Lines)
draw(plt, axis=(; yscale=identity), facet=(; linkyaxes=:minimal))
# easy_save("Alfvenicities"; formats, force=true)
# draw(spec, scales(Layout=(; palette=wrapped(cols=2))); facet=(; linkyaxes=:none))
```

@@

```{julia}
function alpha_layer(df, alpha)
    psp_df = @rsubset(df, :id == "PSP"; view=true)
    thm_df = @rsubset(df, :id == "THEMIS"; view=true)
    wind_df = @rsubset(df, :id == "Wind"; view=true)
    (data(thm_df) + data(wind_df)) * visual(; alpha) + data(psp_df)
end

```

    tdf = @chain df begin
        # @subset(:enc .== enc)
        dropmissing()
        @transform(:L_n_mva = Float64.(ustrip.(:L_n_mva)), :J_m_max_mva = Float64.(ustrip.(:J_m_max_mva)))
        subset_𝐧(𝐧)
    end

    plt = alpha_layer(tdf, 0.618) * visual(Scatter; markersize=6, legend=(; alpha=0.6)) * mapping(color=:id, marker=:id, layout=:id)

    fig = Figure(size=(800, 400))
    axis = (; yscale=log10, xscale=log10)
    v_axis = (; yscale=log10, xscale=log10, limits=((2, 400), (2, 400)))

    ga = fig[1, 1]
    gb = fig[1, 2]
    gc = fig[2, 1]
    gd = fig[2, 2]

    # spec1 = plt * mapping(:Δ𝐁_norm, 𝒎.l_norm) # Not strong correlation
    # spec1 = plt * mapping(:Δ𝐁_norm, 𝒎.j_norm) # Not strong correlation
    spec1 = plt * mapping(𝒎.l, 𝒎.j)
    spec2 = plt * mapping(𝒎.l_norm, 𝒎.j_norm)
    spec3 = plt * mapping(:B_n_mva_norm => L"B_{n}/ B", :ω_in => L"ω_{in}")
    spec4 = plt * mapping(:ΔV_ratio => L"|Δ𝐕| / |Δ𝐕_A|", :ΔV_cosθ => L"\cos \theta")

    grid1 = draw!(ga, spec1; axis)
    draw!(gb, spec2; axis)
    draw!(gc, spec3)
    draw!(gd, spec4; axis=(; limits=((0, 2), (-1, 1),)))

    # pretty_legend!(fig, grid1)
    # add_labels!([ga, gb, gc])
    easy_save("joint_properties-$𝐧"; formats, force=true)
    display(fig)
end
```

@@

    B_n_spec = plt * mapping(:B_n_mva_norm, :ω_in) * AoG.density(npoints=50)
    ΔV_spec = plt * mapping(:ΔV_ratio, :ΔV_cosθ) * (vis + AoG.linear() * ΔV_cosθ_map)
    σc_σr_spec = plt * mapping(:σ_c, :σ_r) * (vis + AoG.smooth() * visual(color=:red))

@@

    draw!(fig[1, 1], B_n_spec; axis)
    draw!(fig[1, 2], ΔV_spec; axis=(; limits=((0, 2), (-1, 1),)))
    draw!(fig[2, 1], σc_σr_spec)
    draw!(fig[2, 2], β_A_He_spec)

@@

```{julia}
view = true
𝒎 = var_mapping(; 𝐧)

vars = [:B_n_mva_norm, :Q_sonnerup, :duration, :σ_c]

tdf = @chain df begin
    dropmissing(vars)
    @rsubset(all(!isnan, (:B_n_mva_norm, :Q_sonnerup, :σ_c)); view=true)
    @transform!(:B_n_mva_norm = Float64.(:B_n_mva_norm))
end

Bn_df = subset_𝐧(tdf, 𝐧)

fig = Figure(; size=(800, 400))
axis = (;)

# layout = mapping(row=:id, col=:enc)
layout = mapping(col=:id)
plt = data(tdf) * layout
den_vis = AoG.density(npoints=50)

# vis = visual(Scatter; markersize=5)
# line_vis = visual(linewidth=3)
# Q_group = mapping(group=:Q_sonnerup => >(0), color=:Q_sonnerup => >(0))
# (vis + AoG.linear() * Q_group * line_vis)
# (vis + AoG.smooth() * A_He_group * line_vis)

Bn_Q_spec = data(Bn_df) * mapping(:B_n_mva_norm => L"B_n/B", :Q_sonnerup => abs  => L"Q") * layout * den_vis
duration_Q_spec = plt * mapping(:duration => log10, :Q_sonnerup => L"Q") * den_vis
σc_Q_spec = plt * mapping(:σ_c => L"σ_c", :Q_sonnerup => L"Q") * den_vis
σr_Q_spec = plt * mapping(:σ_r => L"σ_r", :Q_sonnerup => L"Q") * den_vis

draw!(fig[1, 1], Bn_Q_spec)
draw!(fig[1, 2], duration_Q_spec)
draw!(fig[2, 1], σc_Q_spec)
draw!(fig[2, 2], σr_Q_spec)

# add_labels!([ga, gb, gc])
easy_save("Q_sonnerup_joint_dist_den"; formats, force=true)
display(fig)
```

```{julia}
view = true
𝒎 = var_mapping(; 𝐧)

A_He_df = @chain tdf begin
    dropmissing(:A_He)
    @transform!(:A_He = Float64.(only.(:A_He)))
    @rsubset(:A_He < 10)
end

β_df = @chain df begin
    @rsubset(all(!isnan, [:β, :Q_sonnerup]); view=true)
    dropmissing([:β, :Q_sonnerup])
    @transform!(:log_β = log10.(:β))
end

fig = Figure(; size=(1200, 800))
axis = (;)

layout = mapping(row=:id, col=:enc)
plt = data(tdf) * layout
vis = visual(Scatter; markersize=5)

Q_group = mapping(group=:Q_sonnerup => >(0), color=:Q_sonnerup => >(0))
A_He_group = mapping(group=:A_He => >(0), color=:A_He => >(0))
den_vis = AoG.density(npoints=50)

A_He_Q_spec = data(A_He_df) * mapping(:A_He => log10, :Q_sonnerup => abs) * layout * AoG.density(; npoints=50, datalimits=((-1, 1), (0, 1)))
β_Q_spec = data(β_df) * mapping(:log_β, :Q_sonnerup => abs) * layout * AoG.histogram(; bins=50, datalimits=((-1, 1), (0, 1)))

# draw!(fig[1, 1], Bn_Q_spec)
draw!(fig[3, 1], A_He_Q_spec)
draw!(fig[3, 2], β_Q_spec)

# add_labels!([ga, gb, gc])
# easy_save("Q_sonnerup_joint_dist"; formats, force=true)
display(fig)
```

>>>>

```{julia}
using Dates
using StatsBase, Statistics
using PSPAnisotropy
import Discontinuity as DC
using Discontinuity: var_mapping, compute_params!, filter_low_mva_quality
using Discontinuity: compute_Alfvenicity_params!, Alfven_velocity
using DimensionalData
using DataFrames, DataFramesMeta
using CairoMakie
using Beforerr: _theme_legend, easy_save
using AlgebraOfGraphics
using AlgebraOfGraphics: data
import AlgebraOfGraphics as AoG
using LinearAlgebra
using Accessors
using Unitful
Unitful.preferunits(u"nA", u"km")

# https://github.com/MakieOrg/AlgebraOfGraphics.jl/issues/464
foreach([:log10, :log2, :log]) do f
    @eval import Base: $f
    @eval $f(x::Unitful.Quantity) = $f(ustrip(x))
end
set_Z_theme!()
formats = (:pdf, :png)
```

@@

fs = map([:mva]) do 𝐧
    figure = (; size=(450, 600))
    𝒎 = var_mapping(; 𝐧)

@@

    tdf = @chain df begin
        @subset(.!isnan.(:L_n_mva_norm); view=true)
        subset_𝐧(𝐧)
        dropmissing(:L_n_mva_norm)
    end

    vars = [𝒎.l_log, 𝒎.l_norm_log, 𝒎.j_log, 𝒎.j_norm_log, 𝒎.Δ𝐁, 𝒎.Δ𝐁_norm_log]
    labels = ["Thickness", "Normalized thickness", "Current density", "Normalized current density", "|Δ𝐁|", "|Δ𝐁|/⟨|𝐁|⟩"]
    # append!(vars, [ :Δ𝐁_fit => log10 => "Log Δ𝐁_fit", :Δ𝐁_fit_norm => log10 => "Log Δ𝐁_fit_norm"])
    # append!(labels, ["Δ𝐁_fit", "Δ𝐁_fit_norm"])

    plt = AoG.data(tdf) *
          mapping(vars, layout=AoG.dims(1) => renamer(labels)) *
          mapping(color=:id, linestyle=:enc) *
          AoG.density(; datalimits) * visual(Lines)
    f = draw(plt, scales(Layout=(; palette=wrapped(cols=2))); axis=(; yscale=log10), figure, legend=(; position=:top))
    hide_facet_labels!(f)
    rowgap!(f.figure.layout, 1)
    easy_save("$fname-$𝐧"; formats, force=true)
end
fs[1]
```

@@

Notes: `V_l_ratio_max` and `ΔV_ratio` are pretty much similar

![](../figures/Alfvenicities.png)

```{julia}
update_theme!(;
    Legend=(; framevisible=false, padding=(0, 0, -16, 0)),
)
let
    𝒎 = var_mapping(; 𝐧)
    datalimits = x -> quantile(x, [0.01, 0.99])
    tdf = @chain df begin
        dropmissing(:V_l_ratio)
        @subset(.!isnan.(:V_l_ratio) .&& .!isnan.(:ΔV_cosθ); view=true)
        subset_𝐧(𝐧)
    end

    ΔV_cosθ = :ΔV_cosθ => identity => L"\cos\;θ"
    ΔV_ratio = :ΔV_ratio => identity => L"|Δ𝐕| / |Δ𝐕_A|"
    dB_over_B = :dB_over_B => log10 => L"\text{Log } ΔB / ⟨B\;⟩"
    dB_max_over_B = :dB_max_over_B => log10 => L"\text{Log } ΔB_{\text{max}} / ⟨B\;⟩"
    Q_sonnerup = :Q_sonnerup => abs => ""

    spec = AoG.data(tdf) * mapping(color=:id) *
           AoG.density(; datalimits) * visual(Lines)

    fig = Figure()
    ga = draw!(fig[1, 1], spec * mapping(ΔV_ratio))
    gb = draw!(fig[1, 2], spec * mapping(ΔV_cosθ))
    gc = draw!(fig[2, 1], spec * mapping(dB_over_B))
    gd = draw!(fig[2, 2], spec * mapping(dB_max_over_B))
    add_labels!(fig; valign=:top, position=Left(), padding=(0, 37, 0, 0))
    display(fig)
    pretty_legend!(fig, ga)
    easy_save("Alfvenicities"; formats, force=true)
    # vars = [ΔV_cosθ, ΔV_ratio, dB_over_B, dB_max_over_B]
    # plt = spec * mapping(vars, layout=AoG.dims(1) => renamer(labels))
    # draw(plt, axis=(; yscale=log10), facet=(; linkyaxes=:minimal))
end
```

@@

![](../figures/joint_properties-mva.png)

```{julia}
function alpha_layer(df, alpha)
    psp_df = @rsubset(df, :id == "PSP"; view=true)
    thm_df = @rsubset(df, :id == "THEMIS"; view=true)
    wind_df = @rsubset(df, :id == "Wind"; view=true)
    (AoG.data(thm_df) + AoG.data(wind_df) * visual(; alpha)) + AoG.data(psp_df)
end
```

```{julia}
layout_func(id) = id == "PSP" ? "PSP" : "Wind + THEMIS"

for 𝐧 in [:mva]
    view = true
    𝒎 = var_mapping(; 𝐧)
    tdf = @chain df begin
        dropmissing(:L_n_mva)
        @transform(:L_n_mva = Float64.(ustrip.(:L_n_mva)), :J_m_max_mva = Float64.(ustrip.(:J_m_max_mva)))
        subset_𝐧(𝐧)
    end

    plt = alpha_layer(tdf, 0.3) *
          visual(Scatter; markersize=6, legend=(; alpha=0.6)) *
          mapping(color=:id, marker=:id, layout=:id => layout_func)

    fig = Figure(; size=(400, 800))
    axis = (; yscale=log10, xscale=log10)

    spec1 = plt * mapping(𝒎.l, 𝒎.j)
    spec2 = plt * mapping(𝒎.l_norm, 𝒎.j_norm)
    B_l_spec = plt * mapping(𝒎.Δ𝐁_norm, 𝒎.l_norm) # Not strong correlation
    B_j_spec = plt * mapping(𝒎.Δ𝐁_norm, 𝒎.j_norm) # Not strong correlation

    grid1 = draw!(fig[1, 1], spec1; axis)
    grid2 = draw!(fig[2, 1], spec2; axis)
    grid3 = draw!(fig[3, 1], B_l_spec; axis)
    grid4 = draw!(fig[4, 1], B_j_spec; axis)

    hide_facet_labels!.((grid2, grid3, grid4))

    add_labels!(fig[1:4, 1]; position=Left(), padding=(0, 37, 0, 0))
    display(fig)
    easy_save("joint_properties-$𝐧"; formats, force=true)
end
```

### In-plane rotation angle, Bn

![](../figures/B_n_ω_subset=true.png) and ![](../figures/B_n_ω_subset=false.png)

```{julia}
layout_func(id) = id == "PSP" ? "PSP" : "Wind + THEMIS"

for 𝐧 in [:mva], subset in (true, false)
    normalization = :column
    𝒎 = var_mapping(; 𝐧)
    tdf = dropmissing(df, :B_n_mva_norm)
    tdf = subset ? subset_𝐧(tdf, 𝐧) : tdf
    plt = AoG.data(tdf) * mapping(col=:id => layout_func)
    B_n_ω_spec = plt * mapping(𝒎.bn, 𝒎.ω_in) * fhist(; binedges=(0:0.03:0.99, 0:6:180), normalization)
    f = draw(B_n_ω_spec)
    colgap!(f.figure.layout, 10)

    den_base = AoG.data(tdf) * mapping(color=:id => layout_func) * AoG.density(; datalimits) * visual(Lines)
    ff = f.figure[0, 1:3]
    grid1 = draw!(ff[1, 1], den_base * mapping(𝒎.ω_in))
    grid2 = draw!(ff[1, 2], den_base * mapping(𝒎.bn); axis=(; ylabel="", yscale=log10))
    legend!(ff[1, 1], grid1; tellheight=false, tellwidth=false, halign=:right, valign=:top)
    rowgap!(f.figure.layout, 4)
    add_labels!([ff[1, 1], ff[1, 2], f.figure[1, 1:end]]; position=Left(), padding=(0, 40, 0, -5))
    easy_save("B_n_ω_subset=$subset"; formats, force=true)
end
```

### β vs A_He

There are two populations for beta and alpha particles abundance, corresponding to different sources of solubility. Correlation exist.

@@

    ΔV_spec = plt * mapping(:ΔV_ratio, :ΔV_cosθ) * (vis + AoG.linear() * ΔV_cosθ_map)
    σc_σr_spec = plt * mapping(:σ_c, :σ_r) * (vis + AoG.smooth() * visual(color=:red))

@@

    draw!(fig[1, 2], ΔV_spec; axis=(; limits=((0, 2), (-1, 1),)))
    draw!(fig[2, 1], σc_σr_spec)
    draw!(fig[2, 2], β_A_He_spec)

@@

![](../figures/Q_sonnerup_joint_dist_den.png)

let vars = [:Q_sonnerup, :duration, :σ_c]
    tdf = @chain df begin
        dropmissing(vars)
        @rsubset(all(!isnan, (:ΔV_cosθ, :Q_sonnerup, :σ_c)); view=true)
    end

    fig = Figure(; size=(500, 800))
    plt = AoG.data(tdf) * mapping(col=:id => layout_func)

    Q_limit = (-0.992, 0.992) # mainly for plotting so not show (-1, 1) in ticks
    ΔV_spec = plt * mapping(𝒎.ΔV_ratio, 𝒎.ΔV_cosθ) * AoG.density(; datalimits=((0, 1.1), (-1, 1)))
    duration_Q_spec = plt * mapping(:duration, 𝒎.Q) * AoG.density(; datalimits=((0, 3.1), Q_limit))
    σc_Q_spec = plt * mapping(:σ_c => L"σ_c", 𝒎.Q) * AoG.density()
    σr_Q_spec = plt * mapping(:σ_r => L"σ_r", 𝒎.Q) * AoG.density(; datalimits=(Q_limit, Q_limit))

    ff11, ff12, ff21, ff22 = fig[1, 1], fig[2, 1], fig[3, 1], fig[4, 1]
    grid1 = cdraw!(ff11, ΔV_spec)
    grid3 = cdraw!(ff12, σc_Q_spec)
    grid4 = cdraw!(ff21, σr_Q_spec)
    grid2 = cdraw!(ff22, duration_Q_spec)

    for f in (ff11, ff12, ff21, ff22)
        colgap!(Makie.content(f[1, 1]), 6)
    end

    rowgap!(fig.layout, 4)
    for g in (grid3, grid4)
        ax = g[1].axis
        ax.xlabelpadding[] = 1
        ax.xlabelsize[] = 16
    end
    add_labels!(fig[1:4, 1]; position=Left(), padding=(0, 0, 0, -5))
    hide_facet_labels!.((grid2, grid3, grid4))
    easy_save("Q_sonnerup_joint_dist_den"; formats, force=true)
    display(fig)
end
```

#### Q_sonnerup vs B_n

Two populations for Q_sonnerup vs B_n: large B_n has larger Q_sonnerup. No strong correlation for small B_n groups.

```{julia}
let 𝐧 = :mva
    𝒎 = var_mapping(; 𝐧)
    Bn_df = @chain df begin
        @rsubset(all(isfinite, (:B_n_mva_norm, :Q_sonnerup)); view=true)
        subset_𝐧(𝐧)
    end
    Bn_Q_spec = data(Bn_df) * mapping(𝒎.bn, :Q_sonnerup => L"Q", col=:id => layout_func) * AoG.density()
    draw(Bn_Q_spec)
end
```

#### Q_sonnerup vs A_He

We observe very weak correlation for PSP when $A_{He}<1$, and no correlation for Wind. ![](../figures/A_He_Q_sonnerup.png)

```{julia}
let
    𝒎 = var_mapping()
    A_He_df = @rsubset(df, :A_He > 0, isfinite(:Q_sonnerup))
    A_He_Q_spec = data(A_He_df) * mapping(:A_He, :Q_sonnerup, col=:id => layout_func) * AoG.density(; datalimits=((0, 5), (-1, 1)))
    draw(A_He_Q_spec)
    easy_save("A_He_Q_sonnerup")
end
```

#### Q_sonnerup vs β

No obvious correlation for PSP and Wind ![](../figures/β_Q_sonnerup.png).

```{julia}
let
    β_df = @rsubset(df, all(isfinite, (:β, :Q_sonnerup)); view=true)
    layout = mapping(row=:id)
    β_Q_spec = data(β_df) * mapping(:β => log10, :Q_sonnerup) * layout * AoG.density(; datalimits=((-1, 1), (-1, 1)))
    draw(β_Q_spec)
    easy_save("β_Q_sonnerup")
end
```

### 2025-10-04 notebooks/10_results.qmd
update stats figures with new plots and visualizations

```{julia}
ω_map = :rotation_angle => "rotation angle (deg)";
v_l_ratio_map = :v_l_ratio => L"Δ V_{ion,l} / Δ V_{A,l}"
plt = data(psp_df) * mapping(ω_map, v_l_ratio_map) * (linear() + visual(Scatter))
draw(plt)
```

>>>>

```{julia}
v_l_ratio_map = :v_l_ratio => L"Δ V_{ion,l} / Δ V_{A,l}"
plt = data(psp_df) * mapping(ω_map, v_l_ratio_map) * (linear() + visual(Scatter))
draw(plt)
```
